Mapping Microblog Posts to Encyclopedia Articles

### 2011-02-24 lids/twittersearchwrap/paper/paper.tex

@@

Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years. The idea of micro-blogs is the same as that of blogs, except that the message length is restricted to 140 characters. Twitter has a total of about 190 million of users who produce 65 million twitter messages a day. Thus, twitter represents a huge data source on the web.

Twitter offers the possibility to search for twitter messages containing a specific term or hash tags. This search returns a fixed number of most recent messages containing the search term. However, it is hard to grasp the context of the results and to get further information on the topic that was searched for. As each single twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used. To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds. These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.

On twitter, hash tags are frequently used to associate messages with a specific topic, place, person or evecnt. For example, twitter messages talking about what is going on at the European Semantic Web Conference 2011 will probably be tagged with $\#eswc2011$. If a user encounters this hash tag and does not understand it, he can search for this hash tag. Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result. These tags will help the user to gain an understanding in which context the hash tag is used and what it may mean.
% Konzept von Hashtags genauer erklären? Warum sind Hashtags sinnvoll?
In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities. While it would be more interesting to annotate each single twitter message with relevant entities, twitter messages are too short to contain much relevant information which could be used as input for the annotation tool. Thus, we chose to generate annotations for the whole search result.

The motivation for choosing Wikipedia entities was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).

@@

Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed before: Passant et al. \cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web. They propose a data model which allows for the association of URIs with users, microblogs and microposts. To this end, SIOC and FOAF vocabularies are used and extended. Specifically, the new concepts \emph{Microblog} and {MicroBlogPost} are introduced. Additionally, they propose the use of so-called semantic hash tags. The idea is to use URIs as hash tags (e.g. \emph{\#geo:Paris\_France}). It becomes thus possible to link microposts to entities in the Linked Open Data cloud.

A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
%System beschreiben

@@

The implemented
system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
the Twitter search term and returns a RDF\footnote{\url{http://www.w3.org/RDF/}}
document semantically describing the most recent Twitter messages matching the
given query. The returned RDF document furthermore contains a mapping of the
query to Encyclopedia articles which based on the content published by users that most recently used the search
term in their posts maps to articles best describing the content of Twitter
messages related to the term. An overview of the System Architecture is given in Figure
\ref{fig:arch}.\newline Taking a more detailed look, methods performed by the
Twitter Search Wrapper can be grouped into five sequential steps (see Figure
\ref{fig:arch}). We will follow those steps along a simple example, using
\#ka (a hashtag frequently used to describe posts related to the city of
Karlsruhe, Germany) as search term for the Twitter Search wrapper.

@@

\begin{definition}[Stability]

\end{definition}

>>>>

\newcommand{\myremark}[2]{{\textbf{\marginpar{$\parallel$}(* \textit{#1:} #2 *)}}}

@@

Twitter\footnote{\url{http://twitter.com}} is a micro-blogging service that has become very influential over the last years. The idea of micro-blogs is the same as that of blogs, except that the message length is restricted, in the case of twitter the restriction is 140 characters. Twitter has a total of about 190 million of users who produce 65 million twitter messages a day. Thus, twitter represents a huge data source on the web.

On Twitter it is possible to search for messages containing a specific term or hash tag. This search returns a fixed number of most recent messages containing the search term. However, it is hard to grasp the context of the results and to get further information on the topic that was searched for. As each single twitter message is very short and contains little information, it is necessary to parse the whole set in order to get an overview of the context(s) in which the search term is used. To facilitate this putting into context of the search results, we propose to annotate search results with a set of entities which reflect the content of the result feeds. These entities will not only help to understand the search terms, but also serve as a starting point for refining the search or searching for further information related to the search result.

On twitter, hash tags are frequently used to associate messages with a specific topic, place, person or event. For example, twitter messages talking about what is going on at the European Semantic Web Conference 2011 will frequently be tagged with $\#eswc2011$. If a user encounters this hash tag and does not understand it, he can search for it on twitter. Using our approach the search will not only return messages using the tag but also a set of entities which have been detected in the search result. These tags will help the user to gain an understanding in which context the hash tag is used and what it may mean.

In this paper, we present a system which automatically annotates a Twitter search result with Wikipedia entities. While it would be more interesting to annotate each single twitter message with relevant entities, twitter messages are too short to contain much relevant information which could be used as input for the annotation tool. Thus, we chose to generate annotations for the whole search result.

The motivation for choosing Wikipedia as entity source was that it offers a wide coverage of topics. Furthermore, automatic tools for annotating text with Wikipedia entities are readily available (see \cite{key:wikifier}).

@@

Bringing Semantic Web technologies and Semantic Web technologies together, has been proposed several times.

The SemanticTweet\footnote{\url{http://semantictweet.com}} service is a tool which allows for the generation of a FOAF file describing one's network of followers and friends on Twitter. Thus, an automatic way of mapping the Twitter social network to semantic data is made available.

Passant et al. \cite{key:smob} have proposed a data model for making twitter data available on the Semantic Web. They propose a data model which allows for the association of URIs with users, microblogs and microposts. To this end, SIOC and FOAF vocabularies are used and extended. Specifically, the new concepts \emph{Microblog} and \emph{MicroBlogPost} are introduced. Additionally, they propose the use of so-called semantic hash tags. The idea is to use URIs as hash tags (e.g. \emph{\#geo:Paris\_France}). It becomes thus possible to link microposts to entities in the Linked Open Data cloud via these semantic hash tags.

Softic et al \cite{key:softic} have developed a framework and system for mining data from social networks. They have instantiated their system to analyze data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.

A system for mapping text to Wikipedia entities has been proposed by Milne and Witten \cite{key:wikifier}. 
%uhe: System beschreiben

@@

The goal of our method is to, given a search query as input, provide the user with an RDF\footnote{\url{http://www.w3.org/RDF/} document describing the search result, i.e. the most recent messages that match the query, the authors of these messages and the most relevant entities for this result.

The implemented system\footnote{\url{http://km.aifb.kit.edu/services/twittersearchwrap/}} (further called Twitter Search Wrapper) is called with a query representing
the Twitter search term and returns a RDF}
document semantically describing the most recent Twitter messages matching the
given query. The returned RDF document furthermore contains a mapping of the
query to Encyclopedia articles which based on the content published by users that most recently used the search
term in their posts maps to articles best describing the content of Twitter
messages related to the term. An overview of the System Architecture is given in Figure
\ref{fig:arch}.\newline Taking a more detailed look, methods performed by the
Twitter Search Wrapper can be grouped into five sequential steps (see Figure
\ref{fig:arch}). We will follow those steps along a simple example, using
\#ka (a hashtag frequently used to describe posts related to the city of
Karlsruhe, Germany) as search term for the Twitter Search wrapper.

@@

The goal of our evaluation was to examine the stability of the entity annotations over time. To achieve this, we have repeatedly executed the same set of queries. \myremark{TODO}{How frequently? How long? Which queries?}
In a first step we have filtered the result sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains. We have then evaluated the results with respect to several measures:

\begin{definition}[Evaluation Measures]
Given disjoint result sets $R_1,\ldots,R_n$ for a query $q$ obtained at times $t_1,\ldots,t_n$ and annotated with entities $E_1,\ldots,E_n$, we define:
\begin{itemize}
	\item The average disjoint time $adt$ for a query is the average time that has to lie between two result sets in order to obtain disjoint results: $$adt(q)=\frac{\sum_{i=1}^{n}t_{i+1}-t_i}{n-1}$$
	\item The global stability of the results shows how stable the whole set of entity terms for a query is. It is defined as: $$gs(q)=\frac{\bigcap_{i=1}^{n}E_i}{\bigcup_{i=1}^{n}E_i}$$
	\item The stability for a single term is defined as the fraction of result sets in which it occurs: 
$$st(t)=\frac{|\{i|t\in E_i\}|}{n}$$
\end{itemize}
\end{definition}
